SSA based global code motion of identical computations

### 2017-04-14 hoist.tex
adding Barany and Shobaki

@@

\section{Code hoisting}

The algorithm for code hoisting uses several common representations of the
program that we shortly describe below:
\begin{itemize}
\item Control Flow Graph (\CFG{}) and the Dominance (DOM) and Post-Dominance (PDOM)
  relations \cite{dragonbook};
\item Static Single Assignment (\SSA{}) \cite{cytron};
\item Global Value Numbering (\GVN{}) \cite{rosen1988global,click1995global}: to
  identify similar computations compilers use \GVN{}.  Each expression is given a
  unique number and the expressions that the compiler can prove identical are
  given the same number;
\item Memory \SSA{} \cite{novillo2007memory}: memory operations that the compiler
  is able to prove in dependence are linked through use-def chains.
\end{itemize}

>>>>

Barany \cite{barany2013} presented a global scheduler with ILP formulation with
a goal to minimize register pressure. The results they got were not very
promising. It may be because they only used the scheduler for smaller functions
(<1000 instructions) also they compiled the benchmarks for ARM-Cortex which is
more resilient to register pressure because it has more registers compared to
say X86.

Shobaki \cite{shobaki2013} also recently presented a combinatorial global
scheduler with reasonable performance improvements. It is possible that both
Barany and Shobaki's implmentation will have similar results when compiled for
same target. Also, both suffer the same problem, although Shobaki not so much,
of large compile times which is not feasible for industrial compilers like gcc
and LLVM.

We got reduction in register spills on all the SPEC2006 benchmarks and
reasonable performance improvements with very low compile time overhead.

% TODO: References
% Sink instructions
% Ranking of instructions from Zadeck
% Liveness analysis from Ramakrishna

@@

\section{Code motion}

The algorithm for code motion uses several common representations of the
program that we shortly describe below:
\begin{itemize}
\item Control Flow Graph (\CFG{}) and the Dominance (DOM) and Post-Dominance (PDOM)
  relations \cite{dragonbook};
\item Static Single Assignment (\SSA{}) \cite{cytron};
\item Global Value Numbering (\GVN{}) \cite{rosen1988global,click1995global}: to
  identify similar computations compilers use \GVN{}.  Each expression is given a
  unique number and the expressions that the compiler can prove identical are
  given the same number;
\item Memory \SSA{} \cite{novillo2007memory}: memory operations that the compiler
  is able to prove in dependence are linked through use-def chains.
\end{itemize}
